\textbf{NBA Party}

### 2017-05-05 init_model.rnw
Now using just party variable for prediction in NBA, instead of scaling by avg team age.

### We're only interested in making predictions when teams party.
p <- predict(m, newdata = lines[season == 2017 & nhours.lgame <= HOURS & 
                                last.game.loc != team], type = 'response')
table(round(p), lines[season == 2017 & nhours.lgame <= HOURS & 
                      last.game.loc != team, outcome])

@@

<<echo=1>>=
m <- glm(outcome == 'W' ~ I(nmusicians*(nhours.lgame <= HOURS)/avg.age), 
         data = lines[season < 2017 & last.game.loc != team])

p <- predict(m, newdata = lines[season == 2017 & nhours.lgame <= HOURS & 
                                last.game.loc != team], type = 'response')
table(round(p), lines[season == 2017 & nhours.lgame <= HOURS & 
                      last.game.loc != team, outcome])

@@

<<echo=2:4>>= 
source('functions.r')
m <- glm(I(team.score > opponent.score) ~ party + odds,
         data = lines[year(date) < 2016], family = 'binomial')
p <- predict(m, newdata = lines[year(date) == 2016], type = 'response')

>>>>

### We're only interested in making predictions when teams party.
p <- predict(m, newdata = lines[season == 2017 & nhours.lgame <= HOURS & 
                                last.game.loc != team], type = 'response')

table(round(p), lines[season == 2017 & nhours.lgame <= HOURS & 
                      last.game.loc != team, outcome])

@@

<<echo=1>>=
source('functions.r')
m <- glm(outcome == 'W' ~ party,
         data = lines[season < 2016 & last.game.loc != team])

p <- predict(m, newdata = lines[season == 2016 & nhours.lgame <= HOURS & 
                                last.game.loc != team], type = 'response')

table(round(p), lines[season == 2016 & nhours.lgame <= HOURS & 
                      last.game.loc != team, outcome])

@@

<<echo=2:4>>= 
m <- glm(I(team.score > opponent.score) ~ party + odds,
         data = lines[year(date) < 2016], family = 'binomial')
p <- predict(m, newdata = lines[year(date) == 2016], type = 'response')
